---
title: "frontiermetrics: getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The R package `frontiermetrics` offers a toolbox to detect and map high-level patterns
of deforestation frontiers. These can be defined as the expansion of woodland loss in 
a given area with a high level of spatio-temporal detail (Buchadas et al. 2022). We provide functions to calculate deforestation frontier metrics, based 
on spatio-temporal data provided by Global Forest Watch (Hansen et al. 2013) and a given study area. 

The calculation of frontier metrics is mostly based on the work of Buchadas et al. (2022). 
The package, however, provides greater flexibility on how frontier metrics are 
calculated and classified. Furthermore, the package also include utility functions 
to plot the calculated frontier metrics, derive summary statistics and export the 
metrics to raster layers.

## Obtention of Global Forest Watch data

```{r}
# library(frontiermetrics)
```

```{r, eval = FALSE}
# copo <-  terra::vect(system.file("extdata", "copo.gpkg", package = "multilandr"))
# 
# dir.create("copo_tiles/")
# get_gfw(copo, "copo_tiles/")
```

## Generation of primary dataset

```{r, eval = FALSE}
# gfw_cover <- terra::rast(system.file("extdata", "tree_cover.tif", package = "multilandr"))
# gfw_loss <- terra::rast(system.file("extdata", "loss_year.gpkg", package = "multilandr"))
# 
# copo_dataset <- init_fmetrics(gfw_cover, gfw_loss, year_range = c(2000, 2023), ncores = 2)
```

```{r}
# copo_dataset
```

## Calculation of frontier metrics

```{r, eval = FALSE}
# copo_metrics <- fmetrics(copo_dataset, metrics = "all")
```

```{r}
# copo_metrics
```

```{r, message = FALSE}
# copo_metrics2 <- fmetrics(copo_dataset, metrics = "development")
```

```{r}
# copo_metrics2
```

```{r, message = FALSE}
# copo_metrics3 <- fmetrics(copo_dataset, metrics = "speed")
```

```{r}
# copo_metrics3
```

## Exploratory plotting

## Summary statistics

## Exportation of raster layers

## Setting other parameters

### References

Buchadas, A., Baumann, M., Meyfroidt, P., & Kuemmerle, T. (2022). Uncovering major types of deforestation frontiers across the world’s tropical dry woodlands. Nature Sustainability, 5(7), 619-627.

Hansen, M. C., Potapov, P. V., Moore, R., Hancher, M., Turubanova, S. A., Tyukavina, A., ... & Townshend, J. R. (2013). High-resolution global maps of 21st-century forest cover change. science, 342(6160), 850-853.
